\bf Fast, Scalable Phrase-Based SMT Decoding

### 2016-09-10 amta.2016/amta2016.tex
move to amta.2016

This paper is the first we know of that focuses on improving decoding speed on multicore servers. We will take a holistic approach to solving this issue. We create a decoder that is optimized for multi-core processing speed by concentrating on four main areas.
\begin{enumerate}
  \item \vspace{-2 mm} Faster memory management of data-structures through the use of customized memory pools
  \item \vspace{-2 mm} Exploring alternatives to cardinality-based hypothesis stack configuration
  \item \vspace{-2 mm} Re-examining the efficiency of phrase-table lookup using translation rule caching and data compression
  \item \vspace{-2 mm} Integrating the lexicalized re-ordering model into the phrase-table, thus eliminating the need for independent random lookup this model 
\end{enumerate}
The result is a decoder that is significantly faster than the Moses baseline for single-threaded operation, and scales with the number of cores.

>>>>

This paper is the first we know of that focuses on improving decoding speed on multicore servers. We take a holistic approach to solving this issue, creating a decoder that is optimized for multi-core processing speed by concentrating on four main areas:
\begin{enumerate}
  \item \vspace{-2 mm} Faster memory management of data-structures through the use of customized memory pools
  \item \vspace{-2 mm} Exploring alternatives to cardinality-based hypothesis stack configuration
  \item \vspace{-2 mm} Re-examining the efficiency of phrase-table lookup using translation rule caching and data compression
  \item \vspace{-2 mm} Integrating the lexicalized re-ordering model into the phrase-table, thus eliminating the need for independent random lookup this model 
\end{enumerate}
The result is a decoder that is significantly faster than the Moses baseline for single-threaded operation, and scales with the number of cores.
